%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Kaan Sinar} \\ \vspace{1pt}
    \small 519-760-2269 $|$ \href{mailto:ksinar@uoguelph.ca}{\underline{ksinar@uoguelph.ca}} $|$ 
    \href{https://www.linkedin.com/in/kaan-sinar/}{\underline{linkedin.com/in/kaan-sinar/}} $|$
    \href{https://github.com/ksinar}{\underline{github.com/ksinar}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Guelph}{Guelph, ON}
      {Bachelor of Computing in Computer Science Co-op (Honours)}{Aug. 2019 -- May 2024}
      \resumeItemListStart
        \resumeItem{Dean's Honours List (2020, 2022)}
        \resumeItem{\textbf{Relevant Coursework:} Object-Oriented Programming, Data Structures, Analysis and Design of Algorithms, Software System Development and Integration, Discrete Mathematics, Web Design and Development, Software for Legacy Systems}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- Aug. 2022}
      {Equitable Bank}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Architected and developed a full-stack web application that allows internal employees to query and run stored functions and procedures on a Microsoft SQL Server on-premises.}
        \resumeItem{Designed and implemented the front-end of the application using React and Node.js, and Chakra UI for styling.}
        \resumeItem{Developed the back-end of the application using Node.js and Express.js to handle requests between the front-end and the database.}
        \resumeItem{Optimized the authentication process by implementing Microsoft SSO with Azure Active Directory.}
      \resumeItemListEnd
    \resumeSubheading
      {IT/Software Engineering Intern}{May 2021 -- Jan. 2022}
      {Chicken Farmers of Ontario}{Guelph, ON}
      \resumeItemListStart
        \resumeItem{Developed the Audit Evolution project, which aimed to streamline the auditing process for the on-farm representatives who are auditing the chicken farms using JavaScript framework SAPUI5.}
        \resumeItem{Developed the connection between company's internal portal and Microsoft Dynamics 365 using D365 Web API and Microsoft Graph API.}
        \resumeItem{Transitioned company's back-end from SAP to Dynamics 365.}
        \resumeItem{Collaborated with an external company (Velosio) to create and configure the back-end.}
        \resumeItem{Ran analytics on farmers' data using Python and Power BI.}
      \resumeItemListEnd
    
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{GPX Parser Web App} $|$ \emph{C, Node.js, JavaScript, mySQL, HTML, CSS, Bootstrap, jQuery}}{}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application with Node.js serving a C back-end}
            \resumeItem{Developed a custom C library to parse through the GPS data and store each component in the form of a linked list}
            \resumeItem{Performed calculations on the data to display information about the tracks, routes and waypoints}
            \resumeItem{Used haversine formula to find the distance between two points using the latitudes and longitudes of the points}
            \resumeItem{Used JavaScript(jQuery) to retrieve and display the data on the front-end}
            \resumeItem{Developed connection to the school's mySQL server to allow users to log in through the site and upload or access their own GPX files}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{C\_Shell} $|$ \emph{C}}{}
          \resumeItemListStart
            \resumeItem{Developed my own implementation of a UNIX shell in C}
            \resumeItem{Developed a command line interface with shell prompt that displays current working directory}
            \resumeItem{Implemented piping commands via forks, as well as input and output redirection between commands}
            \resumeItem{Used UNIX libraries to allow user to run commands in the foreground and background, use pipes, and traverse the file system}
          \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{FSreport} $|$ \emph{C, UNIX Libraries}}{}
%           \resumeItemListStart
%             \resumeItem{Developed a C program that calls system libraries to get information on the filesystem at the given directory path and display it in a human readable format}
%             \resumeItem{This information
% includes permissions, ownership, file name, inode number, time last accessed, time last modified, and size}
%             \resumeItem{Implemented bubble sort to sort the output by inode number}
%           \resumeItemListEnd

    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, Java, Python, JavaScript, SQL, PowerShell, Bash (Shell Scripting), HTML, CSS, PHP, R} \\
     \textbf{Frameworks}{: React, Next.js, SAPUI5, WordPress} \\
     \textbf{Developer Tools}{: Git, Node.js, Vim, VS Code, PyCharm, IntelliJ, Eclipse, Postman, PowerBI, Dynamics365, SAP, jQuery} \\
     \textbf{Libraries}{: pandas, NumPy} \\
     \textbf{Technical Skills}{: Web Development, GNU/Linux (Arch), macOS, Windows, SEO, RESTful APIs}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
